---
title: Chapter 7 Lab Non-linear Modeling
editor_options: 
  markdown: 
    wrap: 72
---

```{r}
library(ISLR)
library(MASS)
```


#### 7.8.1 Polynomial Regression and Step Functions ####

Fitting a linear model using a 4th degree polynomial
```{r}
fit = lm(wage ~ poly(age,4), data=Wage)
summary(fit)
```

COMMENT: raw = false
This means that each column of poly() is a linear combination of variables

Coefficients of the 4th degree polynomial
```{r}
coef(summary(fit))
```


Using poly(raw=TRUE)
```{r}
fit2 = lm(wage ~ poly(age, 4, raw=TRUE), data=Wage)
coef(summary(fit2))
```


# Using I() to fit polynomial
```{r}
fit2a = lm(wage ~ age + I(age^2) + I(age^3) + I(age^4), data=Wage)
coef(fit2a)
```


# Using cbind() to fit polynomial
```{r}
fit2b = lm(wage ~ cbind(age, age^2, age^3, age^4), data=Wage)
coef(fit2b)
```


## Getting the range of ages in Wage
```{r}
agelims = range(Wage$age)
```

```{r}
## Creating a sequence of values in between agelims
age.grid = seq(from=agelims[1], to=agelims[2])

## Predicting the wages for the ages in age.grid using fit model
preds = predict(fit, newdata=list(age=age.grid), se=TRUE)

# Getting confidence interval for each prediction
se.bands = cbind(preds$fit+2*preds$se.fit, preds$fit-2*preds$se.fit)

# Plotting the data
par(mfrow=c(1,2), mar=c(4.5, 4.5, 1, 1), oma=c(0,0,4,0))
plot(Wage$age, Wage$wage, xlim=agelims, cex=.5, col='darkgrey')
title("Degree-4 Polynomial", outer=TRUE)
## Plotting the best fit line
lines(age.grid, preds$fit, lwd=2, col="blue")

## Plotting the confidence bands
matlines(age.grid, se.bands, lwd=1, col="blue", lty=3)
```



# Predicting wages using poly(raw=TRUE)
```{r}
preds2 = predict(fit2, newdata=list(age=age.grid), se=TRUE)
# Checking to see if there is a difference in using poly(raw=TRUE)
max(abs(preds$fit-preds2$fit)) # 7.81597e-11 (no difference)
```



# Testing to see which degree of polynomial is sufficient using ANOVA

Fitting 5 different poly fits
```{r}
fit.1 = lm (wage ~ age, data=Wage)
fit.2 = lm (wage ~ poly(age, 2), data=Wage)
fit.3 = lm (wage ~ poly(age, 3), data=Wage)
fit.4 = lm (wage ~ poly(age, 4), data=Wage)
fit.5 = lm (wage ~ poly(age, 5), data=Wage)

# Running ANOVA (pg.116)
anova(fit.1, fit.2, fit.3, fit.4, fit.5)
```


COMMENTS: 
P-values in ANOVA that are around 0.05 is desired. ???? 
  - Too low p-values indeicate that it is not sufficient 
  - Too high p-values indeicate that it is not necessary/justified
Can use ANOVA for both poly(raw=FALSE) or poly(raw=TRUE)


# Viewing the p-values using coefs if poly(raw=FALSE) is used
```{r}
coef(summary(fit.5))
```


# Fitting a model to predict if person receives over 250k or below
```{r}
fit = glm(I(wage>250) ~ poly(age, 4), data=Wage, family=binomial)
```


# Predicting using Logistic Regression
```{r}
preds = predict(fit, newdata=list(age=age.grid), se=TRUE)
```


# Inversing the logits to get probabilities
```{r}
pfit = exp(preds$fit)/(1+exp(preds$fit))
```


# Getting the confidence bands of logits
```{r}
se.bands.logit = cbind(preds$fit+2*preds$se.fit, preds$fit-2*preds$se.fit)

# Getting the confidence bands of probabilities
se.bands = exp(se.bands.logit)/(1+exp(se.bands.logit))

# Predicting using type='response'
preds = predict(fit, newdata=list(age=age.grid), type='response', se=TRUE)

# Plotting
plot(Wage$age, I(Wage$wage>250), xlim=agelims, type="n", ylim=c(0,.2))
points(jitter(Wage$age), I((Wage$wage>250)/5), cex=0.5, pch="|", col="darkgrey")
lines(age.grid, pfit, lwd=2, col="blue")
matlines(age.grid, se.bands, lwd=1, col="blue", lty=3)
```


# Using cut function to apply step function

```{r}
## Cutting age into 4 bins
table(cut(Wage$age,4))
```

Fitting a linear model on each bin
```{r}
fit = lm(wage ~ cut(age,4), data=Wage)
coef(summary(fit))
```


# Splines ####
p293

```{r}
library(splines)
```

Basic functions
B-spline or basis spline
```{r}
fit = lm(wage ~ bs(age, knots=c(25,40,60)), data = Wage)
pred = predict(fit, newdata=list(age=age.grid), se=T)
```


```{r}
plot(Wage$age,Wage$wage, col="gray")

lines(age.grid, pred$fit, lwd=2)
lines(age.grid, pred$fit + 2 * pred$se , lty="dashed")
lines(age.grid, pred$fit - 2 * pred$se , lty="dashed")
```


```{r}
dim(bs(Wage$age, knots = c(25,40,60)))
```

```{r}
#bs(Wage$age, knots = c(25,40,60))
dim(bs(Wage$age, df=6)) # 7 Degrees of freedom, 6 basis functions
attr(bs(Wage$age, df=6), "knots")
```


# Natural Spline ####
```{r}
fit2=lm(wage~ns(age,df=4), data = Wage)

pred2=predict(fit2, newdata=list(age=age.grid), se=T)
```

```{r}
#lines(age.grid, pred2$fit, col="red", lwd=2) # FIXME

plot(Wage$age, Wage$wage, xlim = agelims, cex=.5, col="darkgrey")
title("Smoothing Spline")
fit= smooth.spline(Wage$age, Wage$wage, df=16)
fit2=smooth.spline(Wage$age, Wage$wage, cv = TRUE)
#fit2$df

lines(fit, col = "red", lwd=2)
lines(fit2, col = "blue", lwd=2)
legend("topright", legend=c("16 DF", "6.8 DF"),
       col=c("red", "blue"), lty=1, lwd = 2, cex=.8)
```


# Local Regression ####
# Uses loess
```{r}
attach(Wage)
plot(age, wage, xlim = agelims, cex=.5, col="darkgrey")
title("Local Regression")

fit=loess(wage~age, span=.2,data=Wage)
fit2=loess(wage~age, span=.5,data=Wage)

lines(age.grid, predict(fit,data.frame(age=age.grid)),
      col="red", lwd=2)
lines(age.grid, predict(fit2,data.frame(age=age.grid)),
      col="blue", lwd=2)
legend("topright", legend=c("Span=0.2", "Span=0.5"),
       col=c("red", "blue"), lty=1, lwd = 2, cex=.8)
```


## GAMs ####
p294

```{r eval=FALSE, include=FALSE}
#install.packages("akima")
#install.packages("gam")
```

```{r}
gam1=lm(wage~ns(year,4)+ns(age,5) + education, data=Wage)
#plot.gam(gam1, se=TRUE, col="red")
```

```{r}
library(gam)

gam.m3=gam(wage~s(year,4) + s(age,5) + education, data=Wage)
par(mfrow=c(1,3))
plot(gam.m3, se=TRUE,col="blue")

```

```{r}
library(gam)
plot.gam(gam1, se=TRUE, col="red")
```

```{r}
gam.m1=gam(wage~s(age,5) + education, data=Wage)
gam.m2=gam(wage~year+s(age,5) + education, data=Wage)
anova(gam.m1,gam.m2,gam.m3,test="F")
```

```{r}
summary(gam.m3)
```

```{r}
preds=predict(gam.m2,newdata=Wage)
```

```{r}
gam.lo=gam(wage~s(year,df=4)+lo(age,span=0.7)+education, data=Wage)
plot.gam(gam.lo, se=TRUE, col="green")
```

```{r}
gam.lo.i=gam(wage~lo(year,age,span=0.5)+education,data=Wage)
```

```{r}
library(akima)
plot(gam.lo.i)
```

In order to fit a logistic regression GAM, we once again use the I() function in constructing the binary response variable, and set family=binomial

```{r}
gam.lr=gam(I(wage>250)~year+s(age,df=5)+education, family=binomial,data=Wage)
par(mfrow=c(1,3))
plot(gam.lr,se=T,col="green")
```
p297
```{r}
table(education, I(wage >250))
```

```{r}
gam.lr.s=gam(I(wage>250) ~ year+s(age,df=5)+education, family=binomial, data=Wage, subset=(education!="1. < HS Grad"))
plot(gam.lr.s,se=T,col="green")
```

