---
title: "ISLR Chapter 2 Applied Exercises"
output:
  html_document:
    toc: true
    depth: 2    
---
[ISLR Home](../index.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
#library(ISLR)
```


# Q8 
p54


# 8a
```{r}
college = read.csv("College.csv")
# attach(College)
```

# 8b

fix function

{r, results='hide'}

### Add row names

```{r}
rownames(college)=college[,1] ### Set rownames equal to first column
```

## Remove first column

Remove column 1 because we assigned to rownames.
```{r}
# college[,-1]
college=college[,-1] # 
```

# 8c

```{r}
summary(college)
```

## Correlation Pairs

```{r}
library(ISLR)
pairs(College[,1:10]) # [,1:10] college dataframe didn't work
```

```{r}
plot(College$Outstate, College$Private)
```


```{r}
#rm(college)
detach("package:ISLR", unload=TRUE)

attach(college)
plot(Private, Outstate, xlim=c(0,100), ylim=c(0,100))
```

## 8c iv
```{r, elite_colleges}
Elite=rep("No", nrow(college))
Elite[college$Top10perc > 50] = "Yes"
Elite = as.factor(Elite)
summary(Elite)
```


```{r, plot_elite, fig.align='center', out.width="50%"}
plot(college$Outstate, Elite)
```

```{r, elite_vs_outstate, out.width="50%"}
plot(Elite, college$Outstate)
```

```{r, 4plots}
par(mfrow=c(2,2)) # 4 plots per picture
attach(college)
hist(PhD, breaks = 10, col = 3)
hist(F.Undergrad, breaks = 10)
hist(P.Undergrad, col=2, breaks = 15)
hist(Outstate, col=2, breaks = 15)
```

```{r}
pairs(~ PhD + F.Undergrad + P.Undergrad , college)
```

vi. Continue exploring...

# Q9 Auto

a. Which predictors are quantitative, and which are qualitative.

b. range of each quantitative predictor

```{r, range_examples}
# attach(Auto)
library(ISLR)
range(Auto$mpg)
range(Auto$cylinders)
range(Auto$displacement)
range(Auto$weight)
range(Auto$horsepower)
range(Auto$acceleration)
range(Auto$year)
# range(order)
```

# 9c Mean standard deviation for each quantitative predictor

```{r, 9c}
sd(Auto$mpg)
sd(Auto$cylinders)
sd(Auto$displacement)
sd(Auto$weight)
sd(Auto$horsepower)
sd(Auto$acceleration)
sd(Auto$year)
#View(Auto)
```

# 9d

```{r, 9d}
auto = Auto
tenth = auto[10,]

auto = auto[-c(10:85),]
attach(auto)
sd(mpg)
sd(cylinders)
sd(displacement)
sd(weight)
sd(horsepower)
sd(acceleration)
sd(year)
```

# Q10

```{r, q10}
library(MASS)
head(Boston, n=5)
```
Number of rows and columns

How many rows are in this data set? How many columns? What do the rows and columns represent?

```{r, 10a}
dim(Boston)
```
# 10b

Make some pairwise scatterplots of the predictors (columns) in this data set. Describe your findings.

```{r, 10b}
pairs(Boston)
```

# 10c

Are any of the predictors associated with per capita crime rate? If so, explain the relationship.

```{r, pairs_crim_age}
pairs(~ crim + age, Boston)
```

```{r}
#help(Boston)
pairs(~ crim + age + zn, Boston)
```

## 10c Answer

Age of the housing, Most likely the older the neighborhood, the more experience/ lower income it has with crime

Radial Highways, either criminals has quick getaway or it is so far away from highway that it is not gentrified


# 10d

Do any of the suburbs of Boston appear to have particularly high crime rates? Tax rates? Pupil-teacher ratios? Comment on the range of each predictor.

```{r, 10d}
dim(Boston[Boston$crim >= 20,])
dim(Boston[Boston$tax >= 666,])
dim(Boston[Boston$ptratio >= 20,])
```

# 10e

How many of the suburbs in this data set bound the Charles river?

```{r, 10e}
dim(Boston[Boston$chas==1,])[1]
```

# 10f

What is the median pupil-teacher ratio among the towns in this data set?

```{r, 10f}
median(Boston$ptratio)
```

# 10g

Which suburb of Boston has lowest median value of owner- occupied homes? What are the values of the other predictors for that suburb, and how do those values compare to the overall ranges for those predictors? Comment on your findings.

```{r, 10g}
Boston[Boston$medv == min(Boston$medv),]
```

# 10h

In this data set, how many of the suburbs average more than seven rooms per dwelling? More than eight rooms per dwelling? Comment on the suburbs that average more than eight rooms per dwelling.

```{r, 10h}
dim(Boston[Boston$rm > 7,])[1]
dim(Boston[Boston$rm > 8,])[1]
pairs(Boston[Boston$rm > 8,])
```



