---
title: "ISLR Q4.12 - Power functions"
output:
  html_document:
    toc: true
    depth: 2      
---
[ISLR Home](../index.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question

p172

This problem involves writing functions.
(a) Write a function, Power(), that prints out the result of raising 2 to the 3rd power. In other words, your function should compute 23 and print out the results.

Hint: Recall that x^a raises x to the power a. Use the print() function to output the result.

(b) Create a new function, Power2(), that allows you to pass any two numbers, x and a, and prints out the value of x^a. You can do this by beginning your function with the line
```
> Power2=function(x,a){
You should be able to call your function by entering, for instance,
> Power2 (3 ,8)
```

on the command line. This should output the value of 38, namely, 6, 561.

(c) Using the Power2() function that you just wrote, compute 103, 817, and 1313.

(d) Now create a new function, Power3(), that actually returns the result x^a as an R object, rather than simply printing it to the screen. That is, if you store the value x^a in an object called result within your function, then you can simply return() this result, using the following line:
return()
  
 return(result)
 
The line above should be the last line in your function, before the } symbol.

(e) Now using the Power3() function, create a plot of f(x) = x2. The x-axis should display a range of integers from 1 to 10, and the y-axis should display x2. Label the axes appropriately, and use an appropriate title for the figure. Consider displaying either the x-axis, the y-axis, or both on the log-scale. You can do this by using log=‘‘x’’, log=‘‘y’’, or log=‘‘xy’’ as arguments to the plot() function.

(f) Create a function, PlotPower(), that allows you to create a plot of x against x^a for a fixed a and for a range of values of x. For instance, if you call
```
> PlotPower (1:10 ,3)
```
then a plot should be created with an x-axis taking on values 1,2,...,10, and a y-axis taking on values 13,23,...,103.

***

# 12a

```{r}
# Prints 2^3
Power = function() {
  # 2^3
  x = 2
  a = 3
  total = 1
  for (i in 1:a) {
    total = total * x
  }
  
  print(total)
}
Power()
```



# 12b

```{r}
Power2 = function(x, a) {
  
  total = 1
  for (i in 1:a) {
    total = total * x
  }
  
  print(total)
}
```


# 12c

```{r}
Power2(10,3); 10^3
Power2(8, 17); 8^17
Power2(131,3); 131^3
```


# 12d

```{r}
Power3_old = function(x, a) {
  
  total = 1
  for (i in 1:a) {
    total = total * x
  }
  
  return(total)
}

Power3 = function(x, a) {
  result = x^a
  return(result)
}

x = Power3(2,3); x
Power3_old(1:10, 2)
```


# 12e

```{r}
x = 1:10
y = Power3(x, 2)
plot(x,y)
```

Plot log()
```{r}
plot(x,y, log = "xy")
```

# 12f

```{r}
PlotPower = function(x, a) {
  plot(x, Power3(x, a), xlab = "PlotPower")
  
}

PlotPower(1:10 ,3)
```


