---
title: "ISLR Q10.9 - Hierarchical Clustering on States/USArrests"
output:
  html_document:
    toc: true
    depth: 2    
---
[ISLR Home](../index.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question

Consider the USArrests data. We will now perform hierarchical clustering on the states.

(a) Using hierarchical clustering with complete linkage and Euclidean distance, cluster the states.

(b) Cut the dendrogram at a height that results in three distinct clusters. Which states belong to which clusters?
(c) Hierarchically cluster the states using complete linkage and Euclidean distance, after scaling the variables to have standard deviation one.

(d) What effect does scaling the variables have on the hierarchical clustering obtained? In your opinion, should the variables be scaled before the inter-observation dissimilarities are computed? Provide a justification for your answer.

***

```{r message=FALSE, warning=FALSE}
library(ISLR)
```


```{r}
library(ggdendro) # Better dendrograms
library(ggplot2)
```

# 9a Fitting a hierarchical clustering

```{r}
hc.complete = hclust(
  dist(USArrests),
  method="complete"
)
```


## Summary
```{r}
summary(hc.complete)
hc.complete
```

Dendrogram
```{r}
plot(hc.complete)
```

Better Dendrogram
```{r}
ggdendrogram(hc.complete)
```

# 9b

Cutting the tree to have only three branches (clusters)
```{r}
hc.cut.complete = cutree(hc.complete, 3)
```

Number of observations in each class
```{r}
table(hc.cut.complete)
```

```{r}
hc.cut.complete
```

Plotting dendrogram with abline cutting off at 3 clusters
```{r}
par(mfrow=c(1,1))
plot(hc.complete)
abline(h=150, col="red")
```

Better Dendrogram
```{r}
ggdendrogram(hc.complete)
```

# 9c

Scaling the features
```{r}
USArrests.scaled = scale(USArrests)

# Fitting the scaled features
hc.complete.scaled = hclust(
  dist(USArrests.scaled),
  method="complete"
)
```


## Dendrogram

```{r}
plot(hc.complete.scaled)
```

## Better Dendrogram
```{r}
ggdendrogram(hc.complete.scaled)
```

```{r}
ggdendrogram(hc.complete.scaled, rotate = TRUE, theme_dendro = FALSE)
```

# 9d Cutting to 3 branches

Cutting the tree to have only three branches (clusters)

```{r}
hc.scaled.cut.complete = cutree(hc.complete.scaled, 3)
table(hc.scaled.cut.complete)
```

```{r}
table(hc.scaled.cut.complete, hc.cut.complete)
```


COMMENTS:
Scaling the features changes the results. It decreases the vertical axis.
It might be good to scale the features because if the features are in 
difference range, the model might weight features that have high values
since its a big number even though the value might not have an impact
on result.

## References

- [Dendrograms_ggplot2_R.R](https://rpubs.com/TX-YXL/662586)
