---
title: "Q7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In the chapter, we mentioned the use of correlation-based distance and Euclidean distance as dissimilarity measures for hierarchical clustering. It turns out that these two measures are almost equivalent: if each observation has been centered to have mean zero and standard deviation one, and if we let rij denote the correlation between the ith and jth observations, then the quantity $1 − r_{ij}$ is proportional to the squared Euclidean distance between the ith and jth observations.
On the USArrests data, show that this proportionality holds.

Hint: The Euclidean distance can be calculated using the dist() function, and correlations can be calculated using the cor() function.

```{r}
library(ISLR)
set.seed(1)
```

```{r}
names(USArrests)
```

```{r}
dsc <-  scale(USArrests)
```

```{r}
head(dsc)
```

```{r}
a <- dist(dsc)^2
b <- as.dist(1 - cor(t(dsc)))
summary(b / a)
```

## a
```{r}
a
```

## b

```{r}
b
```

