---
title: "ISLR Q10.11 - Hierarchical Clustering on Gene Expression Data"
output:
  html_document:
    toc: true
    depth: 2     
---
[ISLR Home](../index.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question

On the book website, www.StatLearning.com, there is a gene expression data set (Ch10Ex11.csv) that consists of 40 tissue samples with measurements on 1,000 genes. The first 20 samples are from healthy patients, while the second 20 are from a diseased group.

(a) Load in the data using read.csv(). You will need to select header=F.
(b) Apply hierarchical clustering to the samples using correlation-based distance, and plot the dendrogram. Do the genes separate the samples into the two groups? Do your results depend on the type of linkage used?
(c) Your collaborator wants to know which genes differ the most across the two groups. Suggest a way to answer this question, and apply it here.

***

```{r message=FALSE, warning=FALSE}
#library(ISLR)
#library(tidyverse)
```


# 11a Read Gene Data

```{r}
gene = read.csv("Ch10Ex11.csv", header=FALSE)

dim(gene)

summary(gene)
```


# Calculate correlation-based distance
```{r}
gene.corr.dist = as.dist(1-cor(gene))

# Fitting hierarchiacal clustering
h.clust = hclust(
  gene.corr.dist
)
```


# Plot Dendrogram
```{r}
plot(h.clust)
```


COMMENTS: Based on the dendrogram complete linkage seems like it can be classified into two groups.


# Hierarchiacal clustering: average
```{r}
h.clust = hclust(
  gene.corr.dist,
  method='average'
)
```


# Plot Dendrogram
```{r}
plot(h.clust)
```


COMMENTS: Average Linkage does not separate into two groups


# Hierarchiacal clustering: single
```{r}
h.clust = hclust(
  gene.corr.dist,
  method='single'
)
```


# Plot Dendrogram
```{r}
plot(h.clust)
```


COMMENTS: Single linkage looks like it can separate into two groups but looks 
wacky.


# Hierarchiacal clustering: centroid
```{r}
h.clust = hclust(
  gene.corr.dist,
  method='centroid'
)
```


# Plot Dendrogram
```{r}
plot(h.clust)
```

```{r}
summary(h.clust)
h.clust
```

