---
title: "ISLR Q10.11"
output:
  html_document:
    toc: true
    depth: 2     
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
#library(ISLR)
#library(tidyverse)
```


# 11a Read Gene Data

```{r}
gene = read.csv("Ch10Ex11.csv", header=FALSE)

dim(gene)

summary(gene)
```


## Calculating the correlation-based distance
```{r}
gene.corr.dist = as.dist(1-cor(gene))

# Fitting hierarchiacal clustering
h.clust = hclust(
  gene.corr.dist
)
```


## Plotting a dendrogram
```{r}
plot(h.clust)
```


COMMENTS: Based on the dendrogram complete linkage seems like it can be classified into two groups.


## Fitting hierarchiacal clustering
```{r}
h.clust = hclust(
  gene.corr.dist,
  method='average'
)
```


## Plotting a dendrogram
```{r}
plot(h.clust)
```


COMMENTS: Average Linkage does not separate into two groups


## Fitting hierarchiacal clustering
```{r}
h.clust = hclust(
  gene.corr.dist,
  method='single'
)
```


## Plotting a dendrogram
```{r}
plot(h.clust)
```


COMMENTS: Single linkage looks like it can separate into two groups but looks 
wacky.


## Fitting hierarchiacal clustering
```{r}
h.clust = hclust(
  gene.corr.dist,
  method='centroid'
)
```


## Plotting a dendrogram
```{r}
plot(h.clust)
```

```{r}
summary(h.clust)
h.clust
```

