---
title: "ISLR Chapter 10 Lab 03 - NCI60 Data Example"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

p407

## 

```{r}
library(ISLR)
nci.labs=NCI60$labs
nci.data=NCI60$data
dim(nci.data) # 64 rows and 6,830 columns
```

examine the cancer types for the cell lines

```{r}
nci.labs[1:4]
```

```{r}
table(nci.labs)
```

### PCA on the NCI60 Data

```{r}
pr.out=prcomp(nci.data, scale=TRUE)
```

Function will be used to assign a color to each of the 64 cell lines, based on the cancer type to which it corresponds.
```{r}
Cols=function(vec){
  cols=rainbow(length(unique(vec)))
  return(cols[as.numeric(as.factor(vec))])
}
```

plot the first few principal component score vectors

```{r}
par(mfrow=c(1,2))
plot(pr.out$x[,1:2], col=Cols(nci.labs), pch=19, xlab="Z1", ylab="Z2")
plot(pr.out$x[,c(1,3)], col=Cols(nci.labs), pch=19, xlab="Z1", ylab="Z3")
```

On the whole, cell lines corresponding to a single cancer type do tend to have similar values on the first few principal component score vectors.
summary of the proportion of variance explained (PVE)

```{r}
summary(pr.out)
```
plot the variance explained by the first few principal components
```{r}
plot(pr.out, main="Variance Explained")
```

The height of each bar in the bar plot is given by squaring the corresponding element of pr.out$sdev.

It is more informative to plot the PVE of each principal component (i.e. a scree plot) and the cumulative PVE of each principal component.

```{r}
pve=100*pr.out$sdev^2/sum(pr.out$sdev^2)
par(mfrow=c(1,2))
plot(pve, type="o", ylab="PVE", xlab="Principal Component", col =" blue ")
plot(cumsum(pve), type="o", ylab="Cumulative PVE", xlab="Principal Component ", col =" brown3 ")
```

## Clustering the Observations of the NCI60 Data

this step is optional and should be performed only if we want each gene to be on the same scale.
```{r}
sd.data=scale(nci.data)
```

Perform hierarchical clustering of the observations using complete, single, and average linkage. Euclidean distance is used as the dissimilarity measure.

```{r}
par(mfrow=c(3,1))
data.dist=dist(sd.data)
plot(hclust(data.dist), labels=nci.labs, main="Complete Linkage", xlab="", sub="",ylab="")
plot(hclust(data.dist, method="average"), labels=nci.labs, main="Average Linkage", xlab="", sub="",ylab="")
plot(hclust(data.dist, method="single"), labels=nci.labs, main="Single Linkage", xlab="", sub="",ylab="")
```

Complete and average linkage tend to yield evenly sized clusters whereas single linkage tends to yield extended clusters to which single leaves are fused one by one.

#### Cut height to 4

cut the dendrogram at the height that will yield a particular number of clusters

```{r}
hc.out=hclust(dist(sd.data))
hc.clusters=cutree(hc.out,4)
table(hc.clusters,nci.labs)
```

All the leukemia cell lines fall in cluster 3, while the breast cancer cell lines are spread out over three different clusters.

```{r}
par(mfrow=c(1,1))
plot(hc.out, labels=nci.labs)
abline(h=139, col="red")
```

Printing the output of hclust gives a useful brief summary of the object

```{r}
hc.out
```
#### Commpare kmeans and hierarchical clustering

How do these NCI60 hierarchical clustering results compare to what we get if we perform K-means clustering with K = 4?

```{r}
set.seed(2)
km.out=kmeans(sd.data, 4, nstart=20)
km.clusters=km.out$cluster
table(km.clusters, hc.clusters )
```

We see that the four clusters obtained using hierarchical clustering and K-means clustering are somewhat different

Cluster 2 in K-means clustering is identical to cluster 3 in hierarchical clustering. However, the other clusters differ: for instance, cluster 4 in K-means clustering contains a portion of the observations assigned to cluster 1 by hierarchical clustering, as well as all of the observations assigned to cluster 2 by hierarchical clustering.

perform hierarchical clustering on the first few principal component score vectors
```{r}
hc.out=hclust(dist(pr.out$x[,1:5]))
plot(hc.out, labels=nci.labs, main="Hier. Clust. on First Five Score Vectors")
```


```{r}
table(cutree(hc.out,4), nci.labs)
```

