---
title: "ISLR Chapter 10 Lab 01 - Principal Components Analysis"
output:
  html_document:
    toc: true
    depth: 2     
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

p401

We perform PCA on the USArrests data set, which is part of the base R package. The rows of the data set contain the 50 states, in alphabetical order.

```{r}
states=row.names(USArrests)
#states
names(USArrests)
```

Apply the mean to each column
```{r}
apply(USArrests, 2, mean)
```

Apply the variance to each column
```{r}
apply(USArrests, 2, var)
```

## Perform principal components analysis

Use the prcomp() function.

By default, the prcomp() function centers the variables to have mean zero. By using the option scale=TRUE, we scale the variables to have standard deviation one.

```{r}
pr.out=prcomp(USArrests, scale=TRUE)
summary(pr.out)
```
```{r}
pr.out$center
pr.out$scale
```

```{r}
names(pr.out)
```

The rotation matrix provides the principal component loadings; each column of pr.out$rotation contains the corresponding principal component loading vector.
```{r}
pr.out$rotation
```

There are four distinct principal components. In general min(n - 1, p) informative principal components in a data set with n observations and p variables.

```{r}
dim(pr.out$x)
```
## Plot first two principal components

```{r}
biplot(pr.out, scale=0)
```

The scale=0 argument to biplot() ensures that the arrows are scaled to represent the loadings; other values for scale give slightly different biplots with different interpretations.

## Reproduce Figure 10.1

```{r}
pr.out$rotation=-pr.out$rotation
pr.out$x=-pr.out$x
biplot(pr.out, scale=0)
```

The prcomp() function also outputs the standard deviation of each principal component
```{r}
pr.out$sdev
```

The variance explained by each principal component is obtained by squaring these:

```{r}
pr.var <- pr.out$sdev^2
pr.var
```

To compute the proportion of variance explained by each principal component, we simply divide the variance explained by each principal component by the total variance explained by all four principal components:
```{r}
pve=pr.var/sum(pr.var)
pve
```
We see that the first principal component explains 62.0 % of the variance in the data, the next principal component explains 24.7 % of the variance, and so forth.

## Plot PVE


We can plot the PVE explained by each component,
as well as the cumulative PVE, as follows:

```{r}
par(mfrow=c(1,2))
plot(pve, xlab="Principal Component", 
     ylab="Proportion of Variance Explained ",
     ylim=c(0,1),type='b')
plot(cumsum(pve), xlab="Principal Component ",
     ylab="Cumulative Proportion of Variance Explained ",
     ylim=c(0,1), type='b')
```

cumsum() used above is the cumulative sum.
```{r}
a=c(1,2,8,-3)
cumsum (a)
```
