---
title: "ISLR Q7.8 - Non-Linear Models/Auto"
output:
  html_document:
    toc: true
    depth: 2    
---
[ISLR Home](../index.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question

p299

Fit some of the non-linear models investigated in this chapter to the Auto data set. Is there evidence for non-linear relationships in this data set? Create some informative plots to justify your answer.

***

```{r include=FALSE}
library(tidyverse) 
library(ISLR)
```

```{r}
glimpse(Auto)
```

```{r}
library(skimr)
skim(Auto)
```


```{r echo=FALSE}
attach(Auto) 
pairs(Auto)
```

```{r}
names(Auto)
```

## Cylinders vs MPG
```{r}
g1 <- ggplot(Auto, aes(x = cylinders, y = mpg, group = cylinders)) + geom_boxplot() + theme(legend.position = "none")
g1
```

## Displacement vs MPG
```{r}
ggplot(Auto, aes(x = displacement, y = mpg)) +
  geom_point(alpha = 0.5) +
  geom_smooth()
```

## Horsepower vs MPG

```{r}
ggplot(Auto, aes(x = horsepower, y = mpg)) +
  geom_point(alpha = 0.5) +
  geom_smooth()
```

## Weight vs MPG

```{r}
ggplot(Auto, aes(x = weight, y = mpg)) +
  geom_point(alpha = 0.5) +
  geom_smooth()
```

```{r eval=FALSE, include=FALSE}
?loess
```


## Acceleration vs MPG

```{r}
ggplot(Auto, aes(x = acceleration, y = mpg)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", formula = y ~ x)
```

## Year vs MPG

```{r}
ggplot(Auto, aes(x = year, y = mpg)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", formula = y ~ x) # Default params
```

## Origin vs MPG

```{r}
ggplot(Auto, aes(x = origin, y = mpg, group=origin)) +
  geom_boxplot()# + theme(legend.position = "none")
```


# GAM - Generalize Additive Models

```{r message=FALSE, warning=FALSE}
library(gam)
```

```{r}
# gam.fit = gam(mpg ~ cylinders +  s(acceleration,4) + s(weight,4), data = Auto)
gam.fit = gam(mpg ~ cylinders, data = Auto)
```

## Model Summary
```{r}
summary(gam.fit)
```

# References

- https://www.datanovia.com/en/blog/how-to-plot-a-smooth-line-using-ggplot2/
