---
title: "ISLR Q7.6 - /Wage"
output:
  html_document:
    toc: true
    depth: 2    
---
[ISLR Home](../index.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Question

p299

In this exercise, you will further analyze the Wage data set considered throughout this chapter.

(a) Perform polynomial regression to predict wage using age. Use cross-validation to select the optimal degree d for the polyno- mial. What degree was chosen, and how does this compare to the results of hypothesis testing using ANOVA? Make a plot of the resulting polynomial fit to the data.

(b) Fit a step function to predict wage using age, and perform cross- validation to choose the optimal number of cuts. Make a plot of the fit obtained.

***

```{r message=FALSE, warning=FALSE}
library(ISLR)
library(boot)
```


# 6a

```{r}
# Creating a placeholder for the cv errors
cv.error = rep(0, 5)

# Running a for loop to iterate through each polynomial and fitting data
for (i in 1:5) {
  # Fitting data the polynomial i
  glm.fit = glm(wage ~ poly(age, i), data=Wage)
  
  # Saving the CV estimate for the fit
  cv.error[i] = cv.glm(Wage, glm.fit)$delta[1]
}
```

## Plot CV Error

```{r}
# Plotting the results of for loop
plot(c(1:5), cv.error)
```


Comments:

- Based on the one-SE rule, the cv chooses the 3rd degree polynomial 
- The ANOVA chooses 4th degree polynomial

# 6b

```{r}
cv.error = rep(0, 5)
# Running a for loop to iterate through each step function and fitting data
for (i in 2:5) {
  # Fitting data the polynomial i
  print(i)
  Wage$age.cut = cut(Wage$age, i)
  glm.fit = glm(wage ~ age.cut, data=Wage)
  
  # Saving the CV estimate for the fit
  cv.error[i] = cv.glm(Wage, glm.fit)$delta[2]
}
```

## Plot CV Error

```{r}
plot(c(2:5), cv.error[2:5], pch=20, cex=0.5, lwd=2)
```

