---
title: "ISLR Q3.10 - Multiple Regression/Carseats"
output:
  html_document:
    toc: true
    toc_depth: 2
---
[ISLR Home](../index.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question

p123

This question should be answered using the Carseats data set.

(a) Fit a multiple regression model to predict Sales using Price, Urban, and US

(b) Provide an interpretation of each coefficient in the model. Be
careful - some of the variables in the model are qualitative!

(c) Write out the model in equation form, being careful to handle the qualitative variables properly

(d) For which of the predictors can you reject the null hypothesis $H_0 :\beta_j =0$?

(e) On the basis of your response to the previous question, fit a smaller model that only uses the predictors for which there is evidence of association with the outcome

(f) How well do the models in (a) and (e) fit the data?

(g) Using the model from (e), obtain 95% confidence intervals for the coefficient(s).

(h) Is there evidence of outliers or high leverage observations in the model from (e)?

***

```{r message=FALSE, warning=FALSE}
library(ISLR)
```

# 10a $Sales = \beta_0 + \beta_1 Price + \beta_2 Urban + \beta_3 US$

```{r}
names(Carseats)
carseat.fit = lm(Sales ~ Price + Urban + US, data=Carseats)
```

# 10b Interpret Coefficients

## Model Summary
```{r}
summary(carseat.fit)
```

```{r}
contrasts(Carseats$US)
```

USYes coefficient: If the store is in the US (predictor=1), the sales increase 
at a rate ofthe coefficient is 1.2. 

sales = 1.2 * USYes (1.2 from coefficient from model) (ignoring other predictors for simplicity)

Price: Price is highly significant (p-value) when it comes to sales. There is a slight negative correlation to sales. As prices goes up, sales go down.

UrbanYes: Does not have a significant p-value. This means that it does not effect the sales.
Consider removing from model

# 10c Model with Qualitative Variables

Sales = 13.04 - 0.05 * Price + 1.2 * US
1 if US = Yes ; 0 if US = No

# 10d Reject Predictors/Features

We can reject the null hypothesis for Price and USYes because its p-value is highly significant (<<.05)

# 10e Smaller Model

## Model Summary
```{r}
carseat.fit2 = lm(Sales ~ Price + US, data=Carseats)
summary(carseat.fit2)
```

## Diagostic Plots
```{r}
par(mfrow = c(2,2))
plot(carseat.fit2)
```

# 10f Compare Models

The models for both (a) and (e) do NOT fit the data well. The $R^2$ statistic for both models show that the model ONLY explains 23% of the variance.  

# 10g 95% Confidence Interval

Getting the confidence intervals for each coefficient confint(carseat.fit2)

# 10h Outliers and High Leverage

## Diagnostic Plots
```{r}
par(mfrow = c(2,2))
plot(carseat.fit2)
```

Based on the Residuals vs. Leverage graph (bottom right):

 - There is one observation that is far right of the graph. This means that its leverage is really high. Also there are few more that are few more that have high leverage.

