---
title: "ISLR Q3.12"
output:
  html_document:
    toc: true
    depth: 2
---

[ISLR Home](../index.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This problem involves simple linear regression without an intercept.

```{r message=FALSE, warning=FALSE}
library(ISLR)
```


# 12a

(a) Recall that the coefficient estimate $\hat{\beta}$ for the linear regression of Y onto X without an intercept is given by (3.38). Under what circumstance is the coefficient estimate for the regression of X onto Y the same as the coefficient estimate for the regression of Y onto X?

***

The coefficent estimate for regression of X onto Y will be the same for coefficent 
estimate for regression of Y onto X when the there is no irreducible error and 
there is a perfect linear relationship between x and y (y=x).

## Creating arbitrary data

```{r}
set.seed(0)
x = rnorm(100)
```

# 12b

(b) Generate an example in R with n = 100 observations in which the coefficient estimate for the regression of X onto Y is different from the coefficient estimate for the regression of Y onto X

***

Equation Y onto X

```{r}
y = 2 * x + rnorm(100)
```


## Fitting y onto x without intercept

```{r}
lm.fit.no.intercept = lm(y ~ 0 + x)
summary(lm.fit.no.intercept)
```


## Fitting x onto y without intercept

```{r}
lm.fit.x.y = lm(x ~ 0 + y)
summary(lm.fit.x.y)
```


# 12c

(c) Generate an example in R with n = 100 observations in which the coefficient estimate for the regression of X onto Y is the same as the coefficient estimate for the regression of Y onto X.

***

Equation
```{r}
y = x
```

## Fitting y onto x

```{r}
lm.fit.y.x = lm(y ~ 0 + x)
summary(lm.fit.y.x)
```


## Fitting x onto y

```{r}
lm.fit.x.y = lm(x ~ 0 + y)
summary(lm.fit.x.y)
```



