---
title: "ISLR Q5.9 - /Boston"
output:
  html_document:
    toc: true
    depth: 2      
---
[ISLR Home](../index.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question

p201

We will now consider the Boston housing data set, from the MASS library.

(a) Based on this data set, provide an estimate for the population mean of medv. Call this estimate $\hat{\mu}$.

(b) Provide an estimate of the standard error of $\hat{\mu}$. Interpret this result.

Hint: We can compute the standard error of the sample mean by dividing the sample standard deviation by the square root of the number of observations.

(c) Now estimate the standard error of $\hat{\mu}$ using the bootstrap. How does this compare to your answer from (b)?

(d) Based on your bootstrap estimate from (c), provide a 95% confidence interval for the mean of medv. Compare it to the results obtained using t.test(Boston$medv).

Hint: You can approximate a 95% confidence interval using the formula [$\hat{\mu} − 2SE(\hat{\mu}), \hat{\mu} + 2SE(\hat{\mu})$].

(e) Based on this data set, provide an estimate, μˆmed, for the median value of medv in the population.

(f) We now would like to estimate the standard error of μˆmed. Unfortunately, there is no simple formula for computing the standard error of the median. Instead, estimate the standard error of the median using the bootstrap. Comment on your findings.

(g) Based on this data set, provide an estimate for the tenth percentile of medv in Boston suburbs. Call this quantity $\hat{\mu}_{0.1}$. (You can use the quantile() function.)

(h) Use the bootstrap to estimate the standard error of $\hat{\mu}_{0.1}$. Comment on your findings.

***

```{r message=FALSE, warning=FALSE}
library(MASS)
library(boot)
```


```{r}
names(Boston)
summary(Boston)
dim(Boston)
```

# 9a

Calculating the mean medv for sample 

```{r}
mean.hat = mean(Boston$medv)
print(mean.hat) # 22.5328
```


# 9b

Calculating the standard error of medv
```{r}
sd(Boston$medv)/sqrt(nrow(Boston)) # 0.4089
```


# 9c Bootstrap 

```{r}
boot.fn = function(data, index) {
  return(mean(data[index]))
}

# Using bootstrap to figure out an estimate for population mean
bstrap = boot(Boston$medv, boot.fn, 1000)
print(bstrap) # 0.3994119
```

Comments: The SE of bootstrap is  different from (b) by about 0.001. 

# 9d Creating a 95% confidence interval

```{r}
conf.int = c(bstrap$t0 - (2 * 0.3994119), bstrap$t0 + (2  * 0.3994119))

t.test(Boston$medv)
```

# 9e

```{r}
median_hat = median(Boston$medv)
print(median_hat) # 21.2
```


# 9f

## Calculating median of data

```{r}
boot.median.fn = function(data, index) {
  return(median(data[index]))
}

# Running bootstrap for median
bstrap.median = boot(Boston$medv, boot.median.fn, 10000)
print(bstrap.median) # 0.3754
```


Comments: Median is the same, whether applying boostrap or just median(). The SE, 0.38, is small compared to the median value of 21.2.

# 9g

```{r}
quant.ten = quantile(Boston$medv, probs=c(.1)) # 12.75 
```


# 9h

```{r}
# Calculating 10%  quantile  of data
boot.quant.ten.fn = function(data, index) {
  return(quantile(data[index], probs=c(.1)))
}

# Running bootstrap for median
boot.quant.ten = boot(Boston$medv, boot.quant.ten.fn, 10000)
print(boot.quant.ten) # SE: 0.5027
```


Comments: There was no difference with the 10% quartile, There was a SE of .50.
