---
title: "ISRL Q9.6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(ggthemes) # https://www.datanovia.com/en/blog/ggplot-themes-gallery/
```

p370


At the end of Section 9.6.1 (the Lab), it is claimed that in the case of data that is just barely linearly separable, a support vector classifier with a small value of cost that misclassifies a couple of training observations may perform better on test data than one with a huge value of cost that does not misclassify any training observations. You will now investigate this claim.


### 6a

Generate two-class data with p = 2 in such a way that the classes are just barely linearly separable.

From the lab.  Taking Prince's data generation. FIXME!!
```{r}
set.seed(3154)
# Class one
x.one = runif(500, 0, 90)
y.one = runif(500, x.one + 10, 100)
x.one.noise = runif(50, 20, 80)
y.one.noise = 5/4 * (x.one.noise - 10) + 0.1

# Class zero
x.zero = runif(500, 10, 100)
y.zero = runif(500, 0, x.zero - 10)
x.zero.noise = runif(50, 20, 80)
y.zero.noise = 5/4 * (x.zero.noise - 10) - 0.1
```

# Combine all
```{r}
class.one = seq(1, 550)
x = c(x.one, x.one.noise, x.zero, x.zero.noise)
y = c(y.one, y.one.noise, y.zero, y.zero.noise)

{plot(x[class.one], y[class.one], col = "blue", pch = "+", ylim = c(0, 100))
points(x[-class.one], y[-class.one], col = "red", pch = 4)
}
```

```{r}
df = data.frame(x=x[class.one], y = y[class.one])
df2 = data.frame(x=x[-class.one], y = y[-class.one])

p <- ggplot(df, aes(x=x, y=y, color='black', size=4))
```

+ positive/blue
x negative/red

```{r}
p + geom_point(color='blue', size=3, shape="+") +
  geom_point(data=df2, color='red', size=4, alpha = 1/2, shape=4) + xlim(0, 100)
  #geom_text()
  #xlim(-2, 2) + 
  #ylim(-2, 2) + geom_jitter()
```

### 6b

Compute the cross-validation error rates for support vector classifiers with a range of cost values.

- How many training errors are misclassified for each value of cost considered, 
- how does this relate to the cross-validation errors obtained?

```{r}
library(e1071)
data = data.frame(x=x, y = as.factor(y))

#tune.out = tune(svm, y ~ ., data = dat, kernel="linear", ranges = c(0.1, 1, 5, 100))

tune.out = tune(svm, y ~ ., data = data, kernel="linear", ranges = c(5))
#summary(tune.out)
```


### 6c

Generate an appropriate test data set, and compute the test errors corresponding to each of the values of cost 

- Which value of cost leads to the fewest test errors, 
- How does this compare to the values of cost that yield the fewest training errors and the fewest cross-validation errors?


### 6d

Discuss your results.

