---
title: "ISLR Q9.7 - Support Vector/Auto"
output:
  html_document:
    toc: true
    depth: 2       
---
[ISLR Home](../index.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question

p371

In this problem, you will use support vector approaches in order to predict whether a given car gets high or low gas mileage based on the Auto data set.

(a) Create a binary variable that takes on a 1 for cars with gas mileage above the median, and a 0 for cars with gas mileage below the median.

(b) Fit a support vector classifier to the data with various values of cost, in order to predict whether a car gets high or low gas mileage. Report the cross-validation errors associated with dif- ferent values of this parameter. Comment on your results.

(c) Now repeat (b), this time using SVMs with radial and polyno- mial basis kernels, with different values of gamma and degree and cost. Comment on your results.

(d) Make some plots to back up your assertions in (b) and (c).

Hint: In the lab, we used the plot() function for svm objects only in cases with p = 2. When p > 2, you can use the plot() function to create plots displaying pairs of variables at a time. Essentially, instead of typing

```
> plot(svmfit , dat)
```
where svmfit contains your fitted model and dat is a data frame containing your data, you can type
```
> plot(svmfit , dat , x1∼x4)
```

in order to plot just the first and fourth variables. However, you must replace x1 and x4 with the correct variable names. To find out more, type ?plot.svm.

***

```{r include=FALSE}
library(ISLR)
library(tidyverse)
library(e1071)
```


# 7a

```{r}
mpg.median = Auto$mpg %>% median()
mpg.median
```
```{r}
indicator = ifelse(Auto$mpg > mpg.median, 1, 0)
#indicator
Auto$mpg_above_median = indicator
```

# 7b Linear Kernel

Hyper ... Parameters: Cost
```{r}
tune.out = tune(svm, as.factor(mpg_above_median) ~ weight + displacement, 
                data = Auto,
                kernel = "linear", 
                ranges = list(cost = c(0.01,0.1, 1, 5, 10, 100)))
summary(tune.out)
```

# 7c

**Warning**, if you forget as.factor() the tune() function will hang forever.

## Radial

Parameters: Cost, Gamma
```{r}
kernel <-  "radial"
tune.out.radial = tune(svm, as.factor(mpg_above_median) ~ weight + displacement, 
                data = Auto,
                kernel = kernel, 
                ranges = list(
                  cost = c(0.01,0.1, 1, 5, 10, 100),
                  gamma = c(0.1, 5, 10)
                  ))
summary(tune.out.radial)
```

```{r}
svm.fit.radial = svm(as.factor(mpg_above_median) ~ weight + displacement, data = Auto, kernel = "radial", cost = 5, gamma = 0.1)
#summary(svm.fit.radial)

```

```{r}
svm.fit = svm(as.factor(mpg_above_median) ~ weight + displacement, data = Auto, kernel = "linear", cost = c(1))
#summary(svm.fit)
```

## Polynomial

Parameters: Cost, Degree
```{r}
kernel <-  "polynomial"
tune.out.linear = tune(svm, as.factor(mpg_above_median) ~ weight + displacement, 
                data = Auto,
                kernel = kernel, 
                ranges = list(
                  cost = c(0.01,0.1, 1, 5, 10, 100),
                  degree = c(2,3,4,5)
                  ))
summary(tune.out.linear)
```
```{r}
svm.fit.poly = svm(as.factor(mpg_above_median) ~ weight + displacement,
                   data = Auto, 
                   kernel = "polynomial",
                   cost = .1, degree = 3)
#summary(svm.fit.poly)

```
# 7d

Radial looks the best with the lowest error.
#?plot.svm

## Linear

```{r}
plot(svm.fit, Auto, weight~displacement)
```

## Radial

```{r}
plot(svm.fit.radial, Auto, weight~displacement)
```

## Poly

```{r}
plot(svm.fit.poly, Auto, weight~displacement)
```
